---
title: "Presentation 1"
date: "2020年4月9日"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F)
library(ggplot2)
library(knitr)
library(dplyr)
library(scales)
library(mice)
library(VIM)
require(plyr)
library(kableExtra)
# library(data.table)
library(RColorBrewer)
library(tableone)
library(gridExtra)
library(reshape2)
library(corrplot)
had <- read.csv("HADS/HAD.csv",na.strings = "B")
hads <- read.table("HADS/mice1.csv", header=T, sep=',')
housing <- read.table("HADS/mice1.csv", header=T, sep=',')
rv <- read.csv("HADS/rv.csv", header=F, sep=',')
vars <- colnames(hads)

hads[, c(1:48)] <- as.data.frame(matrix(as.numeric(unlist(hads[, c(1:48)])), ncol=48))

hads$FMTSTRUCTURETYPE <- as.factor(hads$FMTSTRUCTURETYPE)
levels(hads$FMTSTRUCTURETYPE)[1] <- "NA"
hads$FMTSTRUCTURETYPE <- as.character(hads$FMTSTRUCTURETYPE)

nm <- function(x){sum(is.na(x))}
miss.obs1 <- which(apply(hads, 1, nm)==16)
miss.obs2 <- which(apply(hads, 1, nm)==17)
miss.obs3 <- which(apply(hads, 1, nm)==18)
miss <- c(miss.obs1, miss.obs2, miss.obs3)
hads <- hads[-miss, ]
attach(had)
```

## Data Source and Introduction 1
<font size="3">**Name:**</font>

Housing Affordability Data System

<font size="3">**Introduction:**</font>

住房負擔能力數據系統（HADS）是一套住房單位數據集，透過住房單位的地區收入中位數、貧困水平收入和公市場租金，衡量單位的負擔能力和住戶成本。這些數據集的目是為住房分析師提供長期負擔能力和的一致措施。

## Data Source and Introduction 2
<font size="3">**Source:**</font>

United States Department of Housing and Urban Development (HUD) 

<font size="3">**URL:**</font>

<https://catalog.data.gov/dataset/housing-affordability-data-system-hads>.

## Variable Description
解釋變數：45個連續變數，11個類別變數
反應變數：1個連續變數

```{r indep, echo=FALSE}
kable(rv, table.attr='class="table-fixed-header"') %>%
  kable_styling() %>%
  scroll_box(height="450px")

```

## Summary of Variables 1

```{r list, include=FALSE}
cate <- as.vector(vars[which(rv[, 2]==c("Categorical"))]) 
cont <- vars[which(rv[, 2]==c("Continuous"))] 
cattable <- CreateCatTable(vars = cate, data = housing, includeNA = T) 
conttable <- CreateContTable(vars = cont, data = housing, funcNames = c("n", "miss", "p.miss", "mean", "sd", "median", "min", "max")) 
restable <- CreateContTable(vars = "ZINC2", data = housing, funcNames = c("n", "miss", "p.miss", "mean", "sd", "median", "min", "max")) 

a <- print(cattable, showAllLevels = TRUE) 
b <- as.matrix(conttable[["Overall"]]) %>% 
      format(scientific=F) 
c <- as.matrix(restable[["Overall"]]) %>% 
      format(scientific=F) 
``` 

<font size="4">**Categorical Variables**</font>

```{r category, echo=FALSE} 
kable(a, table.attr='class="table-fixed-header"') %>% 
 kable_styling() %>% 
 scroll_box(height="500px") 
``` 

## Summary of Variables 2
 <font size="4">**Continuous Variables**</font> 

```{r continuous, echo=FALSE} 
kable(b, table.attr='class="table-fixed-header"') %>% 
   kable_styling() %>% 
   scroll_box(height="500px") 
``` 

## Summary of Variables 3
<font size="4">**Response Variable to Be Predicted**</font> 

```{r response, echo=FALSE} 
kable(c, table.attr='class="table-fixed-header"') %>% 
 kable_styling() %>%
 scroll_box(height="150px")
``` 

## Research Problem

<font size="4">Predict the affordability of housing</font> 

## Missing Values
missing at random, delete the variable.

```{r missing, echo=FALSE, results=F}
 had.aggrplot<-aggr(had, col=c('lightblue','red'),
                   numbers=TRUE, prop = TRUE, sortVars=TRUE,
                   labels=names(had), cex.axis=.7, gap=3)
```


## EDA Plot: Pie Chart
```{r plot, echo=FALSE}
pie <- function(x){
  d = as.data.frame(table(x))
  d <- d %>%
    # arrange(desc(x)) %>%
    mutate(prop = Freq / sum(d$Freq) *100)
  print(d)

  ggplot(d, aes(x="", y=Freq, fill=x)) +
    geom_bar(stat="identity", width=1, color="white") +
    coord_polar("y", start=0) +
    theme_void() +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Blues")+
    theme(axis.text.x=element_blank())+
    geom_text(aes(label = paste(percent(prop/100),x, sep="\n")), size=5
              , position = position_stack(vjust = 0.5))
}
pie2 <- function(x){
  d = as.data.frame(table(x))
  d <- d %>%
    # arrange(desc(x)) %>%
    mutate(prop = Freq / sum(d$Freq) *100)
  print(d)

  ggplot(d, aes(x="", y=Freq, fill=x)) +
    geom_bar(stat="identity", width=1, color="white") +
    coord_polar("y", start=0) +
    theme_void() +
    # theme(legend.position="none") +
    theme(legend.position = "right") +
    scale_fill_brewer(palette="Blues")+
    theme(axis.text.x=element_blank())+
    geom_text(aes(label = percent(prop/100)), size=5
              , position = position_stack(vjust = 0.5))
}

pie(had$FMTMETRO3)

```

## EDA Plot: Pie Chart 2
```{r plot2, message=F}
pie(had$FMTREGION)
```

## EDA Plot: Pie Chart 3
```{r plot3, message=F}
pie2(had$FMTBURDEN)
```

## EDA Plot : GGPLOT
```{r plot4, message=F}
ggplot(had, aes(x=VALUE)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, fill="#FF6666")
```

## EDA Plot : GGPLOT 1
```{r plot5, message=F}
ggplot(had, aes(x=TOTSAL)) +
  geom_histogram(aes(y=stat(density)), colour="black", fill="white")+
  geom_density(alpha=.2, fill="#FF6666")
```

## EDA Plot : GGPLOT 2
```{r plot6, message=F}
ggplot(had, aes(x=AGE1, color=METRO3)) +
  geom_histogram(aes(y=stat(density)), colour="black", fill="white")+
  geom_density(alpha=.2, fill="#FF6666")
```

## EDA Plot : GGPLOT 3
```{r plot7, ehco=FALSE}
ggplot(had, aes(x=FMTREGION, y=LMED, fill=FMTMETRO3)) +
  geom_boxplot() +
  scale_fill_brewer(palette="Set1") +
  labs(title ="Area Average Income by Metro & Region")
```

## EDA Plot : GGPLOT 4
```{r plot8, ehco=FALSE}
ggplot(had, aes(x=FMTREGION, y=TOTSAL, fill=FMTMETRO3)) +
  geom_boxplot() +
  scale_fill_brewer(palette="Set1") +
  ylim(NA, 2e+05) +
  labs(title ="Wage Income by Metro & Region")
```

## EDA Plot : GGPLOT 5
```{r plot9, ehco=FALSE}
ggplot(had, aes(x=FMTREGION, y=FMR, fill=FMTMETRO3)) +
  geom_boxplot() +
  scale_fill_brewer(palette="Set1") +
  labs(title ="Fair Market Rent by Metro & Region")
```

## EDA Plot : GGPLOT 6
```{r plot10, ehco=FALSE}
ggplot(had, aes(x=FMTREGION, y=VALUE, fill=FMTMETRO3)) +
  geom_boxplot() +
  scale_fill_brewer(palette="Set1") +
  ylim(NA, 1e+06) +
  labs(title ="Current Market Value by Metro & Region")
```

